---
title       : Storm Database Explorer
subtitle    : 
author      : Maciej
job         : 
framework   : revealjs        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []           # {mathjax, quiz, bootstrap}
ext_widgets : {rCharts: libraries/nvd3}
mode        : selfcontained # {standalone, draft}
revealjs:
  theme: simple

--- .custom

# Storm Database Explorer



```{r, echo=FALSE}
library(data.table)
library(rCharts)
library(reshape2)

dt <- fread('data/events.agg.csv')
dt.agg.year <- dt[, list(Count=sum(COUNT), Injuries=sum(INJURIES), Fatalities=sum(FATALITIES)), by=list(YEAR)]
```


--- .custom

## Between 1950 and 2011 severe weather events caused at least

 - `r format(sum(dt$FATALITIES), big.mark=' ')` deaths
 - `r format(sum(dt$INJURIES), big.mark=' ')` injuries
 - $`r format(round((sum(dt$PROPDMG) + sum(dt$CROPDMG)) / 1000), big.mark=' ')` billion worth of damage
 

--- &custom .custom

## Now you can prepare yourself using Storm Database Explorer



 - state of the art user interface*
 - high quality data**
 - fast and reliable***
 - 100% Open source 

- - -

*** =foo

- * If you really determined there is a chance you'll find worse.
- ** There is small chance it could be worse.
- *** It works. Most of the time.

--- .custom

## ... and it can generate cool plots


```{r nvd3plot2, results = 'asis', comment = NA, message = F, echo = F} 

data <- melt(dt.agg.year[, list(YEAR=YEAR, Injuries=Injuries, Fatalities=Fatalities)], id='YEAR')
populationImpact <- nPlot(
    value ~ YEAR, group = 'variable', data = data[order(-YEAR, variable, decreasing = T)],
    type = 'stackedAreaChart', dom = 'populationImpact'
)
        
populationImpact$chart(margin = list(left = 100))
populationImpact$yAxis( axisLabel = "Affected", width = 80)
populationImpact$xAxis( axisLabel = "Year", width = 70)
        
populationImpact
```

--- .custom

## Are you interested?

- visit us on shinyapps.io [(bit.ly/1kLwP06)](http://bit.ly/1kLwP06)
- fork on GitHub ([bit.ly/1nrtceI](http://bit.ly/1nrtceI))
-  enroll on [Coursera Data Science Specialization](https://www.coursera.org/specialization/jhudatascience/1) and learn how to build your own







